Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-18 paper/uist_2016/paper.tex
major edits throughout

\begin{abstract}
We propose \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips. \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from Google's Street View images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed \textit{Rewind} videos offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone. \textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still generating believable representations that capture the past.
\end{abstract}

@@

Capturing a memory is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

While a camera or camcorder can explicitly capture a snapshot of an interesting moment, that one snapshot is only a tiny part of an experience, made even tinier when traveling. In fact, most travel experience happens in transit: the perfectly cloudy stroll from the Eiffel Tower to the Louvre, the sound of dry gravel crackling under bus tires traversing up to Machu Picchu or monsoon rains drumming on all the tin roofs of Hanoi, and even the flight over the Florida Keys on the way to the sun-bathed Caribbean islands. A simple photograph is conclusively lacking in context.

Geolocation data that can be automatically tracked and logged on a smartphone can be used to create context: to look up the weather at each moment, retrieve streetside photos from Google Street View at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features. The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time. The sequences of visuals are stitched together into an interface that allows users to directly manipulate the point in time being shown by scrubbing back and forth (Figure~\ref{fig:scrubbing}). So all a person has to do is enable location tracking on their mobile device to later rewind and re-experience a past trip.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{scroll}
     \caption{Users move the stitched-together images forward and backward in time by scrubbing their pointer.}
     \label{fig:scrubbing}
\end{figure}

Rewind applies a framework for exploring fundamental questions about the human experience. Normally, it is difficult to ask someone about parts of their past that they do not entirely remember, because they do not remember what they do not remember. If you ask someone about a picture of themselves from ten years ago and they do not remember that particular point in time, there are no steps for re-remembering. Using timestamped location data, we investigate whether a more realistic and contextual digital memory can help remind users of times from the past. Perhaps these Rewinds, series of images moving back and forth, can even help the forgetful recover past experiences. This could be done for people who are already tracking their location intentionally (using a smartphone app like Moves or GPSLogger), or for the many people for whom location tracking has been enabled by default on Android phones. The Rewind system generates stitched-together and manipulated photos, called Rewinds, which we use to learn what makes memories memorable, believable, and desirable. Participants in a two-week study looked at their own Rewinds and assessed which trips or places were more memorable, whether the Rewinds felt believable as their own memories, which memories they desired to preserve, and in this process, helped us gain a sense of what Rewinds are beyond static photographs.

We realize that not all memories are equally desirable. Through our study, we discovered not only what factors contribute to making a trip or place more memorable, but whether these are memories worth preserving. Are there aspects of a route that make a person want to review or relive a trip?

@@

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images. However, Rewind differs in that the mapping is finalized with geolocation data provided by lifeloggers tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

@@

\begin{figure}[h]
   \centering
     \includegraphics[width=1\linewidth]{Rewind-Sample-Grid}
     \caption{Rewinds are generated by stitching together Google Street View images of consecutive points on a given route. They are played from left to right to simulate a person on the move.}
     \label{fig:rewinds}
\end{figure}

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. %\ref{fig:flowchart}

@@

\subsubsection{Route Determination} (needs to be rephrased? perhaps?)
A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record. \textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX. Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user. First, the user uploads their geolocation data to Rewind's main page. From there, less accurate location records are filtered out using the accuracy ratings provided by Google. Any location recording that has an accuracy radius greater than 200 meters is ignored. The accepted data is stored in memory to prepare the user's location points. A location frequency map is generated by counting the number of times each location appears in history. In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances. The location with the highest number of visits is marked as user's home. We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.

\subsubsection{Hyperlapse Creation} 
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser. Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incorporate a large training dataset into the rendering pipeline. Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

As the Google Street view images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex. the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times). Thus sky and ground regions could be approximated by generalizing the observed geographical information of the incoming images. Each pixel was first converted from RGB representation into HSV color space. For seasonal changes, a range of HSV values was estimated for plantation classification and those HSV values that fell within the range were adjusted for desired seasonal effects. Each HSV value was then converted back to RGB color space for JavaScript canvas painting (Figure~\ref{fig:season}). Similarly, for creating nightly effects such as sunset and evening scenes, sky colors were modified using the same technique. In addition, two linear brightness and saturation filters were applied locally and globally (Figure~\ref{fig:timeofday}). As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1. Approximated sky region 2. Non-sky region in the approximated sky region 3. Approximated Ground region. RGB values of each pixel were down-scaled based on the region the pixel is classified in.

For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (currently only available for images from [anonymized: our state/province]). Sky colors was adjusted again using the technique mentioned previously for overcast, rainy and snowy sky. For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the hyperlapse and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}).

@@

Users can click on the images to load the accompanying ``trip'' videos (stitched images), or Rewinds. The purpose of Rewinds is to help users remember locations and trips. Rewinds are composed of locations visited on the same date as the Rewind's corresponding image. When the user loads a Rewind, all the locations the user visited on that day are gathered and sorted, after which a route is mapped between the locations using the Google Maps API. This route data is passed to StreetviewSequence to generate Rewinds by stitching together images. For each point on a given route, StreetviewSequence requests panorama data from Google and determines the appropriate pitch and heading values to get the correct portion of the panorama. Those values are sent to Google Street View along with the necessary geolocation data to get the images that will be stitched together to make the Rewind.

In order to account for time of day and season changes, StreetviewSequence library is modified to allow Rewind to intercept and manipulate each frame of the trip video, similar to the manipulations applied to the 10 location images. Once all the images within a trip are gathered from Google Street View and processed with CamanJS, users can play Rewinds in a loop, or scrub forward and backward over the video to investigate individual images more closely.

\section{User Study}
\subsection{Research Questions}
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where someone has been. To start to understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photography. By comparing Rewinds to today's most prevalent form of digital memory media, we can begin to distill what features make a Rewind meaningful and representative as a memory of a trip.

Our research questions examine the effectiveness of Rewinds through three aspects: memorability, believability, and desirability.

1) Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable?

2) Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?

3) Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?

\subsection{Participants}
Participants for the user study were recruited online through local Craigslist classifieds and Reddit communities for the Providence area. Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women. Participants ranged from ages 20 to 50. Most participants were local residents, with occupations including librarian, medical researcher, office worker, IT consultant, musician, and comedian. A fifth of the participants were undergraduate or graduate students.

@@

At the in-person interview, participants were shown a series of photos and accompanying Rewinds that represented the trips they took during the tracking period. The participant's geolocation data was trimmed to ensure that photos and Rewind videos were generated from data gathered no earlier than the past two weeks. Participants were shown ten photo-Rewind pairs.  Of the ten pairs, five showed trips taken infrequently, three showed trips taken most frequently, and the remaining two were random.

At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with. Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.

For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data. The participant was asked to answer the following questions about the photo:

Do you remember this location? If so, can you name the street? Can you name what is around the location, such as buildings, landmarks, or other places?

Would you want to keep this photo? Why or why not? Were you traveling alone?

If you remember the location, is the photo accurate to your memory? Why or why not? What was different?

The participant was then shown a Rewind of the trip that they were on when the previous location was encountered. While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace. The participant was asked the following questions while the Rewind played:

Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?

Would you want to keep this video? Why or why not? Were you traveling alone?

If you remember these locations, is the video accurate to your memory? Why or why not? What was different?

Questions about the photos and Rewinds tested their memorability, believability, and desirability as memory media.

In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.

The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 cash for their time at the end of the study.

@@

\subsubsection{Travel Companions}
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were much more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

@@

\subsubsection{Frequent Travelers}
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were much more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

@@

\subsubsection{GPS Usage}
Our results show that participants who were not regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did. Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, "I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road," when asked about the accuracy of a trip.

@@

\subsection{Desirability and Value}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. In general, participants did not want to. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

Overall, participants wanted to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

\subsubsection{Participant Responses}
When asked why they wanted to keep or not keep a photo or Rewind, patterns emerged in the participants' answers. Participants didn't want to keep anything that was "no use" or had "no meaning or significance." One participant said they "didn't need any more memories of work." Some participants acknowledged the "good composition," and one said, "It's not a bad photo but it wasn't taken by me." Participants were most likely to keep photos that reminded them of good memories,

\subsection{Participant Reactions}
There was a range of behaviors and attitudes toward Rewinds from the participants. One participant called Rewinds "creepy, eerie," and said they might "show them to a friend who's a conspiracy theorist." Another participant proclaimed that they weren't "paranoid about technology." Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip. Other participants did not feel positive after watching their Rewinds, saying that they "just realized how often [they] take the same route," or that they felt like they "needed to switch up [their] routine." One participant was amazed, and exclaimed, "It's like it's happening!" But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: "I recognize the photo now." The Rewind had helped them remember the location of the original image.

@@

While the study results provide a wealth of correlations between varying factors and participant groups, our most significant findings pertain to the effects of regular GPS usage, visit frequency, and travel companionship on Rewind memorability, believability, and desirability.

>>>>

\begin{abstract}
We introduce \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips. \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed \textit{Rewind} videos offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone. \textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

@@

Capturing a memory is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, a prototype of the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

While a camera or camcorder can explicitly capture a snapshot of an interesting moment, that one snapshot is only a small part of an experience, made even smaller when traveling. In fact, most travel experience happens in transit: the perfectly cloudy stroll from the Eiffel Tower to the Louvre, the sound of dry gravel crackling under bus tires traversing up to Machu Picchu or monsoon rains drumming on all the tin roofs of Hanoi, and even the flight over the Florida Keys on the way to the sun-bathed Caribbean islands. A simple photograph lacks this type of context.

Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment, retrieve street side photos (e.g. from Google Street View) at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features. The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time. The sequences of visuals are stitched together into an interface that allows users to directly manipulate the point in time being shown by scrubbing back and forth (Figure~\ref{fig:scrubbing}). So all a person has to do is enable location tracking on their mobile device to later rewind and re-experience a past trip.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{scroll}
     \caption{Users move the stitched-together sequences of images forward and backward in time by scrubbing their pointer.}
     \label{fig:scrubbing}
\end{figure}

Rewind applies a framework for exploring fundamental questions about the human experience. Normally, it is difficult to ask someone about parts of their past that they do not entirely remember, because they do not remember what they do not remember.
% Note from Jeff: I'm not a fan of this example (that I commented out) because Rewinds don't recreate pictures of you either. Photos are actually much better at doing this.
% If you ask someone about a picture of themselves from ten years ago and they do not remember that particular point in time, there are no steps for re-remembering.
Using timestamped location data, we investigate whether a more realistic and contextual digital memory can help remind users of times from the past. Perhaps these Rewinds, sequence of images moving back and forth, can even help the forgetful recover past experiences. This could be done for people who are already tracking their location intentionally (using a smartphone app like Moves or GPSLogger), or for the many people for whom location tracking has been enabled by default on Android phones.

Through Rewind, we investigate what makes memories memorable, believable, and desirable. Participants in a two-week study looked at their own Rewinds and assessed which trips or places were more memorable, whether the Rewinds felt believable as their own memories, which memories they desired to preserve, and in this process, helped us gain a sense of what Rewinds are beyond static photographs. But not all memories are equally desirable. Through our study, we discovered not only what factors contribute to making a trip or place more memorable, but whether these are memories worth preserving. Are there aspects of a route that make a person want to review or relive a trip?

@@

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images. However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

@@

\begin{figure}[h]
   \centering
     \includegraphics[width=1\linewidth]{Rewind-Sample-Grid}
     \caption{Rewinds are generated by stitching together Google Street View images of consecutive points on a given route, which are manipulated to match the conditions from the past point in time. Rewinds are played from left to right to simulate a person on the move.}
     \label{fig:rewinds}
\end{figure}

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used). The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. The current version of \textit{Rewind} is a web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. %\ref{fig:flowchart}

@@

\subsection{Route Selection}
A user's geolocation tracking data includes latitude and longitude coordinates, and timestamps of when the user was at given coordinates. \textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX. Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.

When the user loads their location data into Rewind, it filters out location coordinates with < 200 meter accuracy, and a location frequency map is generated by counting the number of times each location appears in history. In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances. The location with the highest number of visits is marked as user's home. Rewind then uses the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.

\subsection{Sequence Creation} 
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images. Considering each \textit{Rewind} sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline. Due to the timing constraint, Rewind instead adopts a simplified approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

As the Google Street View images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex. the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times). Thus sky and ground regions could be approximated by generalizing the observed geographical information of the incoming images. Each pixel was first converted from RGB representation into HSV color space. For seasonal changes, a range of HSV values was estimated for plantation classification and those HSV values that fell within the range were adjusted for desired seasonal effects. Each HSV value was then converted back to RGB color space for JavaScript canvas painting (Figure~\ref{fig:season}). Similarly, for creating nightly effects such as sunset and evening scenes, sky colors were modified using the same technique. In addition, two linear brightness and saturation filters were applied locally and globally (Figure~\ref{fig:timeofday}). As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1) Approximated sky region 2) Non-sky region in the approximated sky region 3) Approximated Ground region. RGB values of each pixel were down-scaled based on the region the pixel is classified in.

For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (for the study, only data from [anonymized: our state/province] was loaded). Sky colors were adjusted again using the technique mentioned previously for overcast, rainy and snowy sky. For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the sequence of images and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}). Note that in the user study reported in this paper, an earlier version of the image manipulation was used, which adjusted whole-image color attributes.

@@

Users can click on the images to load the accompanying ``trip'' videos (stitched sequence of images), or Rewinds. The purpose of the Rewinds is to help users remember locations and trips.
% Note from Jeff: Cut this sentence because I don't understand it. What's a ``corresponding image''?
% Rewinds are composed of locations visited on the same date as the Rewind's corresponding image.
When the user loads a Rewind, all the locations the user visited on that day are gathered and sorted, after which a route is mapped between the locations using the Google Maps API.
% Note from Jeff: Reader doesn't know what StreetviewSequence is, and probably does not need to
% This route data is passed to StreetviewSequence to generate Rewinds by stitching together images. For each point on a given route, StreetviewSequence
For each point in the route, Rewind determines the appropriate pitch and heading values to get the correct portion of the panorama. Those values are sent to Google Street View along with the necessary geolocation data to retrieve images that will be stitched together to make the Rewind.

In order to account for time of day and season changes,
% StreetviewSequence library is modified to allow Rewind to
Rewind intercepts and manipulate each frame of the trip video, similar to the manipulations applied to the 10 location images. Once all the images within a trip are gathered from Google Street View and processed with CamanJS, users can play Rewinds in a loop, or scrub forward and backward over the video to investigate individual images more closely.

\section{User Study}
\subsection{Research Questions}
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been. To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos. By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.

Our research questions examine the effectiveness of Rewinds through three virtues of a memory: memorability, believability, and desirability.

\begin{enumerate}
\item Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable? 
\item Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
\item Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
\end{enumerate}

\subsection{Participants}
To recruit a diverse local population, participants for the user study were recruited online through local forums (Craigslist classifieds and local Reddit communities). Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women, and ranged from 20 to 50 years old. Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
% Jeff notes, comment this out because it's not remarkable
% A fifth of the participants were undergraduate or graduate students.

@@

At the in-person interview, participants were shown a series of photos and accompanying Rewinds that represented the trips they took during the tracking period. The participant's geolocation data was trimmed to ensure that photos and Rewind videos were generated from data gathered no earlier than the past two weeks. Participants were shown ten photo-Rewind pairs in a semi-structured interview.  Of the ten pairs, five showed trips taken infrequently, three showed trips taken most frequently, and the remaining two were random.

At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with.
Then, questions about the photos and Rewinds investigated their memorability, believability, and desirability.

%Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.
For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data. The participant was asked to answer the following questions about the photo: Do you remember this location? If so, can you name the street? Can you name what is around the location, such as buildings, landmarks, or other places? Would you want to keep this photo? Why or why not? Were you traveling alone? If you remember the location, is the photo accurate to your memory? Why or why not? What was different?

The participant was then shown a Rewind of the trip that they were on when the previous location was encountered. While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace. The participant was asked the following questions while the Rewind played: Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places? Would you want to keep this video? Why or why not? Were you traveling alone? If you remember these locations, is the video accurate to your memory? Why or why not? What was different?

In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind. The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.

@@

\subsubsection{Travel Companions}
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

@@

\subsubsection{Frequent Travelers}
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

@@

\subsubsection{GPS Usage}
Our results show that participants who were not regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did. Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.

@@

\subsection{Desirability and Value}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown. Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.

\subsubsection{Participant Responses}
When asked why they wanted to keep or not keep a photo or Rewind, patterns emerged in the participants' answers. Participants didn't want to keep anything that was ``no use'' or had ``no meaning or significance.'' One participant said they ``didn't need any more memories of work.'' Some participants acknowledged the ``good composition,'' and one said, ``It's not a bad photo but it wasn't taken by me.'' Participants were most likely to keep photos that reminded them of good memories,

\subsection{Participant Reactions}
There was a range of behaviors and attitudes toward Rewinds from the participants. One participant called Rewinds ``creepy, eerie,'' and said they might ``show them to a friend who's a conspiracy theorist.'' Another participant proclaimed that they weren't ``paranoid about technology.'' Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip. Other participants did not feel positive after watching their Rewinds, saying that they ``just realized how often [they] take the same route,'' or that they felt like they ``needed to switch up [their] routine.'' One participant was amazed, and exclaimed, ``It's like it's happening!'' But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: ``I recognize the photo now.'' The Rewind had helped them remember the location of the original image.

@@

While the study results provide a wealth of correlations between varying factors and participant groups, our most significant findings pertain to the effects of regular GPS usage, visit frequency, and travel companionship on Rewind memorability, believability, and desirability. Regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability. This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}. We found that while GPS users had lower remembrance overall, the group experienced a jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.
